---
title: "Knapsack Problem"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab06)
```
# Description
This Package gives several solutions to solving the knapsack problem.The knapsack problem or rucksack problem is a problem in combinatorial optimization: Given a set of items, each with a weight and a value, determine the number of each item to include in a collection so that the total weight is less than or equal to a given limit and the total value is as large as possible. 
Some of which are Greedy approach, Dynamic approach and the brute force algorithm.

-----

## Brute Force algorithm (with parallelize)
Brute Force Algorithms refers to a programming style that does not include any shortcuts to improve performance, but instead relies on sheer computing power to try all possibilities until the solution to a problem is found.Here we have implemented this algorithm to solve the knapsack problem.


### Example

```r
# code for parallelize
 if(parallel==TRUE){
    cores <- parallel::detectCores()
    y <- list(knapsack_objects[1:n2,],knapsack_objects[(n2+1):n1,],knapsack_objects[(n1+1):n3,],knapsack_objects[(n3+1):n,])
    result <- parallel::mclapply(y,brute_force_knapsack,W,mc.cores = cores)
  }
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
```

----

## Dynamic algorithm
Dynamic Programming is mainly an optimization over plain recursion. Wherever we see a recursive solution that has repeated calls for same inputs, we can optimize it using Dynamic Programming.

### Example

```r
knapsack_dynamic (x = knapsack_objects[1:8,], W = 2000)
```
----

## Greedy algorithm
A greedy algorithm is any algorithm that follows the problem-solving heuristic of making the locally optimal choice at each stage with the intent of finding a global optimum.

### Example
```r
greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)
```
-----
